---
title: "DATAs project"
author: "DATAs"
date: "10/5/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

First, make sure your working directory is set to the path on your desktop that contains the dataset. If you don't have the dataset, here is the link to download it:
https://www.kaggle.com/spscientist/students-performance-in-exams

You can set this by doing "Session" -> "Set Working Directory" -> "Choose Directory..."


Load the csv file into our dataframe variable. (df stands for dataframe)
```{r warning = FALSE, message = FALSE}
df = read_csv("StudentsPerformance.csv")
```


head() allows us to look at the first 6 rows of the data.
```{r}
head(df)
```
Replace spaces between words in column names with an underscore. 
This will make typing the variables names out to be easier
```{r}
colnames(df) = gsub("[^[:alnum:]]", "_", tolower(colnames(df))); colnames(df)
```



cor() gives us the correlation between the two variables we input. '$' is useful for extracting the particular variable from the dataframe. 
```{r}
cor(df$reading_score, df$writing_score)
```


Plotting writing score against reading score using plot(). We can see that these two variables are highly correlated!
```{r}
plot(df$reading_score, df$writing_score)
```

Plot it... but make it fancier with ggplot().
Also, add a linear regression line. 

geom_point() gives the scatter plot and
geom_smooth() gives the linear regression line
```{r}
ggplot(df, aes(x = writing_score, y = reading_score)) +
  geom_point(color = "blue") +
  geom_smooth(method = 'lm', formula = y ~ x, color = "red")
```

